\documentclass[11pt,a4paper,sans]{moderncv}

% Auther : Kaihang JI
% Github Repo: https://github.com/mimicji/Bilingual-Resume-Template
% Requirement: XeLaTeX

% 使用方法:
%   ***必须使用XeLaTeX编译***
%   撰写简历时：在\CN{}内填写中文内容，后其紧跟的\EN{}内填写英文内容
%   导出时: 选择[Chinese]为中文版，选择[English]为英文版
\usepackage[Chinese]{languageSelection} % 导出中文版
%\usepackage[English]{languageSelection} % 导出英文版

\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{fontawesome5}
\usepackage{zh_CN-Adobefonts_external}

\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}

%**************************************************
%*                 从这里开始                       *
%**************************************************

% 你的双语姓名
\name{付亚鹏}{Ya-Peng(Evan)Fu}

\begin{document}
\makecvtitle
\vspace*{-10mm}

% 个人title
\begin{center}
\vspace*{-5mm}
\CN{
    \textbf{经济学博士在读}
}
\EN{
    \textbf{Ph.D. student in Economics}
}
\end{center}


% 联系方式
\begin{center}
\begin{tabular}{ c c c }
\faPhone\enspace +86 15611577833 & \enspace
\faWeixin\enspace {yapeng_f} & \enspace
\faHome\enspace 
\CN{北京，中国} \EN{Beijing, CN} \\
\faEnvelope 1:\enspace
\color{blue} 
\href{mailto:yapengf@outlook.com}
{yapengf@outlook.com} & \enspace
\faEnvelope 2:\enspace \color{blue}  \href{mailto:1696966846@qq.com}
{1696966846@qq.com} & \enspace \faLink
\enspace \color{blue} 
\href{https://yapengf.com}
{yapengf.com}
\end{tabular}
\end{center}

% 以上项目如需增减，则其它可选图标为：
% \faWhatsapp         % Whatsapp
% \faTwitter          % Twitter
% \faLinkedin         % Linkedin
% \faLine             % Line
% \faFacebookSquare   % Facebook
% \faInstagram        % Instagram
% \faZhihu            % 知乎
% 更多图标见: https://mirrors.ibiblio.org/CTAN/fonts/fontawesome5/doc/fontawesome5.pdf

\begin{center}
    \CN{更新于: \today } \EN{Latest Update: \today}
\end{center}
% 个人简介
\CN{
    \section{个人简介}
    {个人简介内容。
    }
}
\EN{
    \section{Profile}
    {Profile.
    }
}
% 教育经历
\CN{\section{\faBookOpen \enspace 教育经历}}
\EN{\section{\faBookOpen \enspace Education}}

\CN{
\customcventry{09/2024 - 06/2029}
{{中国社会科学院大学}}
{经济学博士}{北京, 中国}{}{}
}
\EN{
\customcventry{09/2024 - 06/2029}
{{University of University of Chinese Academy of Social Sciences}}
{Ph.D. in economics}{Beijing, China}{}{}
}

\CN{
\customcventry{09/2020 - 06/2024}
{{中国社会科学院大学}}
{经济学学士}{北京, 中国}{}{}
}
\EN{
\customcventry{09/2020 - 06/2024}
{{University of University of Chinese Academy of Social Sciences}}
{B.S. in economics}{Beijing, China}{}{}
}

\begin{center}
    \CN{以下内容仍在更新，敬请期待！} \EN{The following are still being updated, so stay tuned!}
\end{center}

% 发表论文
\CN{
    \section{专业领域}
    {内容营销 - WordPress - 内容策略 - 搜索引擎排名 - 数据分析 - 使用高级图表进行可视化 - 社交媒体 - 电子邮件营销 - 用户体验 - 数字策略 - 活动管理 - 领先生成}
}
\EN{
    \section{Areas of Expertise}
    {Content Marketing - WordPress - Content Strategy - Search Engine Ranking - Data Analysis - Visualizing with Advanced Charts - Social Media - Email Marketing - User Experience - Digital Strategy - Campaign Management - Lead Generation}
}


% 工作论文
\CN{ \section{工作经历} }
\EN{\section{Professional Experience} }

\CN{
\customcventry{06/2023 ‐ 至今}{{\color{blue}\href{https://google.com/}{(Stellar Systems)}}}{数字营销策略师,}{北京，中国}{}{
    {\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
    \item 为邮件、社交媒体、SEO/SEM和展示广告技术跨平台活动制定战略计划。
    \item 开发并实施数字营销策略，2023年创造收入超过\$850,000。
    \item 监督执行SEO、SEM、电子邮件、社交媒体和展示广告活动，实现了每次获取成本降低12\%。
    \end{itemize}}}
}
\EN{
    \customcventry{06/2023 ‐ present}{{\color{blue}\href{https://google.com/}{(Stellar Systems)}}}{Digital Marketing Strategist,}{Beijing, CN}{}{
    {\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
    \item Developed strategic plans for campaigns across email, social media, SEO/SEM, and display advertising techniques.
    \item Developed and implemented digital marketing strategies that generated over \$850,000 in revenue in 2023
    \item Oversee the execution of SEO, SEM, email, social media, and display advertising campaigns, achieving a 12\% decrease in cost per acquisition
    \end{itemize}}}
}

\CN{
    \customcventry{01/2023 ‐ 05/2023}{{\color{blue}\href{https://www.google.com/}{(Synapse Solutions)}}}{数字账户经理,}{北京，中国}{}{
    {\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
    \item 实施电子商务业务的重新定向活动等促销活动。
    \item 通过谷歌Adwords监控PPC广告活动的表现。
    \item 管理和优化PPC广告活动，使点击率提高了5％。
    \end{itemize}}}
}
\EN{
    \customcventry{01/2023 ‐ 05/2023}{{\color{blue}\href{https://www.google.com/}{(Synapse Solutions)}}}{Digital Account Manager,}{Beijing, CN}{}{
    {\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
    \item Implemented promotional activities such as re-targeting campaigns for e-commerce businesses.
    \item Monitored the performance of PPC campaigns through Google Adwords. 
    \item Managed and optimized PPC campaigns, resulting in a 5\% increase in click-through rates
    \end{itemize}}}
}


% 学术活动
\CN{\section{在线课程\&证书}}
\EN{\section{Online Courses \& Certifications}}
{\begin{itemize}[label=\textbullet]
\item 
\CN{
数字营销简介（2023年1月）
}
\EN{
Introduction to Digital Marketing (Jan. 2023) 
}
- \underline{\color{blue}\href{https://google.com/}{SEMRUSH}}

\item 
\CN{
LinkedIn数字营销职业必备（2022年8月）
}
\EN{
Career Essentials in Digital Marketing by LinkedIn (Aug. 2022)
}
- \underline{\color{blue}\href{https://google.com/}{LinkedIn}}

\end{itemize}} 




% 荣誉
\CN{\section{专业技能}}
\EN{\section{Skills}}
{\begin{itemize}[label=\textbullet]

\item {
    \CN{
        \textbf{数据可视化:} Microsoft Power BI, Excel
    }
    \EN{
        \textbf{Data Visualization:} Microsoft Power BI, Excel
    }
}

\item {
    \CN{
        \textbf{软件:} Project (MSP), Adobe PhotoShop, Audition, Canva
    }
    \EN{
        \textbf{Software:} Project (MSP), Adobe PhotoShop, Audition, Canva
    }
}
\end{itemize}}


% 专业技能
\CN{\section{语言}}
\EN{\section{Languages}}

\begin{multicols}{2}
    \begin{itemize}[label=\textbullet]
    \item 
        \CN{\textbf{中文} [母语]}
        \EN{\textbf{Mandarin Chinese} [Native]}
    \item 
        \CN{\textbf{英文} [大学英语四级]}
        \EN{\textbf{English} [CET-4]}
    \end{itemize}
\end{multicols}
\end{document}

% This template is edited from: 
% -  https://www.overleaf.com/latex/templates/modern-simple-ats-friendly-latex-cv/fqxnznxhvdgp 
% - https://github.com/xiangrongjingujiu/resume-template